---
title: "EDS 221: Day 7 Interactive Session"
author: "IMS"
format: html
editor_options: 
  chunk_output_type: console
---

```{r}
library(tidyverse)
library(palmerpenguins)
library(lubridate)
```


2. Data wrangling refresher
Refresher 1: Starting with the penguins dataset in the palmerpenguins package, write a single piped sequence in which you:

Only include penguins at Biscoe and Dream islands
Remove the year and sex variables
Add a new column called body_mass_kg, with penguin mass converted from grams to kilograms
Rename the island variable to location


```{r}
penguins |> 
  filter(island  %in% c("Biscoe", "Dream")) |> 
  select(!c(sex, year)) |> 
  mutate(body_mass_kg = body_mass_g/1000) |> 
  rename(location = island)
```


Refresher 2: Staring with the penguins dataset in the palmerpenguins package, write a single piped sequence in which you:

Limit to only Adelie penguins
Remove any observations where flipper_length_mm is NA (hint: !is.na())
Group the data by sex
Find the mean (mean()), standard deviation (sd) and sample size (n) of flipper_length_mm for male and female Adelie penguins, returned in a nice summary table

```{r}
penguins |> 
  filter(species=="Adelie") |> 
  filter(!is.na(flipper_length_mm)) |> 
  group_by(sex) |> 
  summarise(mean = mean(flipper_length_mm),
            sd = sd(flipper_length_mm),
            count = n())
  
```

